### 2019-11-27 Computational Finance/cf_ch_02.rmd
mathematical statistics, ch4
mathematical statistics, ch4

---
title: ''
mainfont: Arial
fontsize: 12pt
documentclass: report
header-includes:
- \PassOptionsToPackage{table}{xcolor}
- \usepackage{caption}
- \usepackage{amssymb}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage[table]{xcolor}
- \usepackage{fancyhdr}
- \usepackage{boldline}
- \usepackage{tipa}
   \definecolor{headergrey}{HTML}{545454}
   \definecolor{msdblue}{HTML}{1C93D1}
   \pagestyle{fancy}
   \setlength\headheight{30pt}
   \rhead{\color{headergrey}\today}
   \fancyhead[L]{\color{headergrey}Moretz, Brandon}
   \fancyhead[C]{\Large\bfseries\color{headergrey}Exploratory Data Analysis}
   \rfoot{\color{headergrey}Chapter 2}
   \lfoot{\color{headergrey}}
   \fancyfoot[C]{\rmfamily\color{headergrey}Mathematical Statistics}
geometry: left = 1cm, right = 1cm, top = 2cm, bottom = 3cm
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
editor_options: 
  chunk_output_type: console
---

@@

#### Chapter 1

### Ex 1.1

We shall use the __getSymbols__ function in the quantmod package to retrieve financial data for General Electric (__GE__).

@@

getSymbols("GE", src = "yahoo", from = "2000-01-01", to = "2009-12-30")

names(GE)

GE["2000-01-01/2000-01-20"]

geAdj = GE$GE.Adjusted["2000-01-01-/2000-01-20"]; geAdj

max(geAdj); min(geAdj); mean(geAdj)

@@

```{r echo = T, fig.height=3.5}
chartSeries(GE)
```

```{r echo = T, fig.height=3.5}
chartSeries(GE, TA=NULL, subset='2001-01::2001-02')
```

```{r echo=T}
saveRDS(GE, file = "GE.rds")
```

>>>>

---
title: ''
mainfont: Arial
fontsize: 12pt
documentclass: report
header-includes:
- \PassOptionsToPackage{table}{xcolor}
- \usepackage{caption}
- \usepackage{amssymb}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage[table]{xcolor}
- \usepackage{fancyhdr}
- \usepackage{boldline}
- \usepackage{tipa}
   \definecolor{headergrey}{HTML}{545454}
   \definecolor{msdblue}{HTML}{1C93D1}
   \pagestyle{fancy}
   \setlength\headheight{30pt}
   \rhead{\color{headergrey}\today}
   \fancyhead[L]{\color{headergrey}Moretz, Brandon}
   \fancyhead[C]{\Large\bfseries\color{headergrey}Statistics of Financial Time Series}
   \rfoot{\color{headergrey}Chapter 2}
   \lfoot{\color{headergrey}}
   \fancyfoot[C]{\rmfamily\color{headergrey}Computational Finance}
geometry: left = 1cm, right = 1cm, top = 2cm, bottom = 3cm
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
editor_options: 
  chunk_output_type: console
---

@@

#### Chapter 2

### Ex 2.1

Consider the curve drawn by the price history of the Dow Jones Industrial Average (DJIA) from 1960 to 2010.

@@

getSymbols("DJIA", src = "yahoo", from = "1960-01-01") ## DJIA from 1896

plot(DJIA['1960/2010'], main = "DJIA")

@@

```{r echo = T, fig.height=3.5}

getSymbols("AAPL", src = "yahoo")
aplRd <- periodReturn(AAPL, period = "daily")
plot(aplRd, main = "APPLE Daily Returns")
```

```{r, echo = T}
x <- seq(-4, 4, 0.01)
plot(x, dnorm(x, mean = 0.5, sd = 1.3), type = "l")
```

```{r, echo=T}

### 2019-11-27 Mathematical Statistics/ms_ch_04.rmd
mathematical statistics, ch4
mathematical statistics, ch4

>>>>

Consider the population {1, 2, 5, 6, 10, 12}.

Find (and plot) the sampling distribution of medians for samples of size 3 without replacement.

```{r, echo = T, fig.height=4.5, fig.width=8}

p <- c(1, 2, 5, 6, 10, 12)
c <- combinations(v = p, n = 6, r = 3)
m <- apply(c, 1, median)

ggplot(data.table(value = m), aes(value, fill = ..count..)) +
   geom_histogram(bins = 30) +
   labs(title = "Median Sampling Distribution of p")

Compare the median of the population to the mean of the medians.

Median of p = __`r median(p)`__. Mean of Medians of p = __`r mean(m)`__

### 4.2

Consider the population {3, 6, 7, 9, 11, 14}.

For samples of size 3 without replacement, find (and plot) the sampling distribution for the minimum.

What is the mean of the sampling distribution?

The statistic is an estimate of some parameter - what is the value of that parameter?

```{r, echo = T}

p <- c(3, 6, 7, 9, 11, 14)
